Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-08 edubots_surveys.Rnw
rev conclusions - list
- Removed duplicates
- Simplified text

From a qualitative point of view, these results show consensus in a few key aspects:
\begin{itemize}
 \item Teachers want to have support from their corresponding institution. This
   is probably due to the strict European data regulations \textcolor{black}{on data protection},
   but also to avoid the overhead required to \textcolor{black}{sign up new students every year.
   In general support from specific formation and access to IT help desk for specific features
   enhances the possibility of adoption by the teachers or the possibility of a successful
   adoption that improves the learning outcomes. This is supported by the result of the two
   surveys: they prefer whatever "messaging" application is provided by the university, and
   also they value sustainability as well as "officiality" of the platform, as shown in
   Table \ref{tab:interaction}}.
 \item Teachers need sustainability. The main reason is that implementing
   changes is expensive in terms of effort and prone to errors in the first
   years of implementing new procedures, therefore, it is logical that if
   chatbots or messaging platforms are to be introduced, they want this change
   to be as permanent as possible.
 \item Keep it Simple. Media interaction requirements are simple and only a 2.4\% is requesting more features. This could be a sign of technological burn out produced by the previous and current courses where, due to the pandemic, the use of computer has increased significantly.
\end{itemize}

>>>>

From a qualitative point of view, these results show consensus in a few key aspects:
\begin{itemize}
 \item Teachers want to have support from their institutions. This
   is probably due to the strict European data regulations on data protection,
   but also to avoid the overhead required to sign up new students every year.
   In general, additional support with specific formation and access to IT help desk for specific features
   enhance the possibility of a successful adoption that improves the learning outcomes. This is supported by the result of the two
   surveys: they prefer whatever "messaging" application is provided by their university, and
   they the "officiality" of the platform, as shown in
   Table \ref{tab:interaction}.
 \item Teachers need sustainability. The main reason is that implementing
   changes is expensive in terms of effort and prone to errors in the first
   years. Therefore, it is logical that if
   chatbots or messaging platforms are to be introduced, teachers want this change
   to be as permanent as possible.
 \item Keep it Simple. Media interaction requirements are simple and only 2.4\% of teachers are requesting more features. This could be a sign of technological burnt out produced by the previous pandemic courses, when the use of computers significantly increased.
\end{itemize}
